---
title: "p1805 HW1 by AK4598"
author: "Aleya Khalifa"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

First, I load the `moderndive` package and the `early_january_weather` dataset. I will show my code throughout.

```{r}
library(moderndive)

data("early_january_weather")
```

This dataset reflects hourly weather data for three New York City airports during the month of January 2013. The dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The columns consist of the variables, `origin` (the weather station emitting the data - in this case, just EWR airport), `year`, `month`, `day`, `hour`, `temp` (temperature), `dewp` (dewpoint), `humid` (humidity), `wind_dir` (wind direction), `wind_speed`, `wind_gust`, `precip` (precipitation in inches), `pressure` (sea level pressure), `visib` (visibility in miles), and `time_hour` (the date/time of the recording). 

```{r}
mean_temp = mean(pull(early_january_weather, temp))
```

Using the above code, the mean temperature reported in this dataset is `r round(mean_temp, digits=2)`.

Below is a scatterplot of `temp` (y) vs. `time_hour` (x). 

```{r}
scatter = ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point()

scatter
```

The color legend reflects _relative humidity_. We can see a cyclical relationship between temperature and time, in that temperatures decrease each night and rise again each day. However, over the entire period, average daily temperatures are increasing. Finally, humidity was lowest at the beginning of the period and highest between January 10-14.

The scatterplot is saved in the project directory. 

```{r, echo = FALSE, message = FALSE}
ggsave("scatter.png", plot = scatter)
```

# Problem 2

## Create a dataframe.
```{r}
df = 
  tibble(
    random_samp = rnorm(10, mean=0),
    logical = random_samp>0,
    character = c("dave",
                  "anshana",
                  "janan",
                  "harry",
                  "kiki",
                  "john",
                  "george",
                  "amir",
                  "max",
                  "gabriella"),
    factor = as.factor(c("low",
                         "middle",
                         "high",
                         "low",
                         "middle",
                         "high",
                         "high",
                         "middle",
                         "high",
                         "low"))
  )
```

## Try taking the mean of each variable in the dataframe.

It works for the `random_samp` variable.
```{r}
mean(pull(df,random_samp))
```

It works for the logical variable, but the output is not exactly a _mean_. It is a representation of the proportion of rows that are TRUE.
```{r}
mean(pull(df,logical))
```


It does not work for the character variable...
```{r}
mean(pull(df,character))
```

... or the factor variable.
```{r}
mean(pull(df,factor))
```


